---
title: "Hatchling production estimation using Richards functions"
output: pdf_document
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(lubridate)
library(readr)
library(reshape2)
library(jagsUI)
library(bayesplot)

source("Dunstan_functions.R")

col.def <- cols(Date = col_date(format = "%m/%d/%Y"),
                Counts_100m = col_double(),
                Season = col_integer(),
                Sector = col_character())

data.1 <- read_csv(file = "data/Hatchling_Data_v3.csv",
                   col_types = col.def)

# These two need to be changed when different runs are used
Day1 <- "12-20"
Day2 <- "04-30"

n.days <- as.numeric(as.Date(paste0("2018-", Day2)) - as.Date(paste0("2017-", Day1)))

seasons <- unique(data.1$Season)

data.1 %>% mutate(DOSeason = as.numeric(Date - as.Date(paste0(Season, "-", Day1)))) -> data.3
```

This is a preliminary analysis and results may change in the future. 

In this document, I describe the steps I used to estimate the number of annual hatchling production from several observations during each nesting season at six sectors (2014R, 2017R, North, South, West, 2019R) on Raine Island. In a separate analysis, I fitted various functions to hatchling counts and found that using modified Richards functions (Girondot et al. 2007) provided the most precise estimates.  Results of the comparison of these models are available upon request.  

# Modified Richards equation by Girondot et al. (2007)

In this approach, I used the model described by Girondot et al. (2007). It has two symmetrical functions that are connected at the peak of nesting.  

The function has the following form:

M1 = (1 + (2 * exp(K) - 1) * exp((1/(-S)) * (P - d))) ^ (-1/exp(K))

M2 = (1 + (2 * exp(K) - 1) * exp((1/S) * (P - d))) ^ (-1/exp(K))

N = min_N + (max_N - min_N) * (M1 * M2), where

d is the number of days from the beginning of nesting season,

S defines the "fatness" of the function (S > 0),

K > 0 defines the "flatness" at the peak of the function (K > 0),

P defines where the peak is relative to the range of d, where min(d) < P < max(d),

min_N is "the basal level of nesting outside the nesting season" and,

max_N >> min_N

This model was fitted to observed hatchling counts per 100 m in each sector and estimated parameters (S, K, P) and their uncertainties were used to compute the total number of hatchlings and its uncertainties from each sector.  


```{r Model_Girondot, include=FALSE, echo=FALSE}
jm <- readRDS(paste0("RData/Girondot_Par_estimation_dnorm_", Day1, "_", Day2, "_2021.rds"))

Sectors <- unique(data.3$Sector)
Girondot_stats <- list(length = 5)
i <- j <- k <- 1
#k <- 50
for (j in 1:length(Sectors)){
  tmp.mat <- matrix(data = NA, nrow = n.days * length(seasons), ncol = 5)
  c <- 1
  for (i in 1:length(seasons)){
    
    for (k in 1:n.days){
      tmp <- Girondot_fcn(k, 
                          extract.samples("S", jm$samples), 
                          extract.samples("K", jm$samples), 
                          extract.samples(paste0("P[", i, "]"), jm$samples), 
                          1, 
                          extract.samples(paste0("max[", i, ",", j, "]"), jm$samples)) 
      tmp.mat[c, ] <- c(seasons[i], k, quantile(tmp, c(0.025, 0.5, 0.975)))
      c <- c + 1  
    }
  }
  tmp.df <- data.frame(tmp.mat)
  tmp.df$Sector <- as.factor(Sectors[j])
  colnames(tmp.df) <- c("Season", "DOSeason", "Xs_q2.5", "Xs_q50", "Xs_q97.5", "Sector")
  Girondot_stats[[j]] <- tmp.df
}

names(Girondot_stats) <-paste0("Xs_", Sectors)

```


Although no formal goodness-of-fit test was conducted, the functions fit qualitatively reasonable to the data (Figure 1).  The fitted function, then, was used for each combinatin of a sector and a season to estimate the number of hatchlings per 100 m. Because the parameters of the function were shared among sectors, estimates were available even when there were limited data (this extrapolation is not presented in this report). 

```{r Girondot_plotEstimates, echo=FALSE, include=TRUE, warning=FALSE,fig.width=8, fig.height=6, fig.cap="Figure 1. The fitted functions (medians in solid lines and their 95% CIs in shaded areas) and observed numbers of hatchlings (dots) per 100 m at six sectors."}
Girondot.all.data <- do.call(rbind, Girondot_stats)

p.fig1 <- ggplot() + 
  geom_path(data = Girondot.all.data,
            aes(x = DOSeason, 
                y = Xs_q50,
                color = as.factor(Season)),
            size = 1.2) +
  geom_ribbon(data = Girondot.all.data , 
                aes(x = DOSeason,
                    ymin = Xs_q2.5, 
                    ymax = Xs_q97.5,
                    fill = as.factor(Season)),
              alpha = 0.3,
              show.legend = F) +  
  geom_point(data = data.3,
             aes(x = DOSeason, 
                 y = (Counts_100m),
                 color = as.factor(Season)),
             size = 2, shape = 16) +
  facet_wrap(Sector ~., nrow = 3, scales = "free") + 
  labs(x = paste0("Days since ", Day1),  
       y = "Median counts and 95% CI",
       color = "Season") +
  guides(color = guide_legend(title.position = "top",
                              title.hjust = 0.5,
                              nrow = 2)) +
  theme(axis.text = element_text(size = 12),
        legend.position = "top", #c(0.75, 0.1),
        axis.title = element_text(size = 12),
        legend.direction = "horizontal")


plot(p.fig1)
```

```{r Girondot_extrapolation, echo=FALSE, warning=FALSE, fig.width=8, fig.height=6, fig.cap="Figure 2. Extrapolated total hatchling abundance at six sectors using estimated Richards function. Year-sector combinations with little or no data were excluded from computing the hatchling abundance."}
Girondot_summary <- summary.stats.nolog.2021(Girondot_stats)

Girondot.total.summary <- Girondot_summary %>% 
  select(Season, total_q2.5, total_q50, total_q97.5, Sector)%>%
  mutate(SeasonNum = as.numeric(Season) + 2013)


Girondot.total.summary[((Girondot.total.summary$SeasonNum < 2017 |
                           Girondot.total.summary$SeasonNum > 2018) & 
                          Girondot.total.summary$Sector == "2017R"),
                   c("total_q2.5", "total_q50", "total_q97.5")] <- NA

Girondot.total.summary[(Girondot.total.summary$Sector == "2019R" & 
                          Girondot.total.summary$SeasonNum < 2019), 
                       c("total_q2.5", "total_q50", "total_q97.5")] <- NA

Girondot.total.summary[(Girondot.total.summary$Sector == "West" & 
                          (Girondot.total.summary$SeasonNum < 2017 |
                             Girondot.total.summary$SeasonNum > 2018)), 
                       c("total_q2.5", "total_q50", "total_q97.5")] <- NA

# Girondot.total.summary[(Girondot.total.summary$Season != "2017" & Girondot.total.summary$Sector == "2017R"),
#                    c("total_q2.5", "total_q50", "total_q97.5")] <- NA

p.fig2 <- ggplot(data = Girondot.total.summary) + 
  geom_point(aes(x = Season, y = (total_q50))) + 
  geom_errorbar(aes(x = Season, 
                    ymin = (total_q2.5), 
                    ymax = (total_q97.5))) +
  facet_wrap(Sector ~., nrow = 2 ) + 
  ylab("Median total hatchling and 95% CI")

plot(p.fig2)
```


```{r Girondot_summaryTable, echo=FALSE, warning=FALSE}
Girondot.total.summary %>% select(Season, total_q50, Sector) -> Girondot.total.median
Girondot.total.summary %>% select(Season, total_q2.5, Sector) -> Girondot.total.q2.5
Girondot.total.summary %>% select(Season, total_q97.5, Sector) -> Girondot.total.q97.5

total.median.wide <- as.data.frame(reshape2::acast(Girondot.total.median, 
                                                   Sector ~ Season, 
                                                   value.var = "total_q50"))

total.q2.5.wide <- as.data.frame(reshape2::acast(Girondot.total.q2.5, 
                                                 Sector ~ Season, 
                                                 value.var = "total_q2.5"))

total.q97.5.wide <- as.data.frame(reshape2::acast(Girondot.total.q97.5, 
                                                  Sector ~ Season, 
                                                  value.var = "total_q97.5"))

total.wide <- data.frame(Sectors = row.names(total.median.wide),
                         "2014" = total.median.wide$`2014`,
                         "2014_L" = total.q2.5.wide$`2014`,
                         "2014_H" = total.q97.5.wide$`2014`,
                         "2015" = total.median.wide$`2015`,
                         "2015_L" = total.q2.5.wide$`2015`,
                         "2015_H" = total.q97.5.wide$`2015`,
                         "2016" = total.median.wide$`2016`,
                         "2016_L" = total.q2.5.wide$`2016`,
                         "2016_H" = total.q97.5.wide$`2016`,
                         "2017" = total.median.wide$`2017`,
                         "2017_L" = total.q2.5.wide$`2017`,
                         "2017_H" = total.q97.5.wide$`2017`,
                         "2018" = total.median.wide$`2017`,
                         "2018_L" = total.q2.5.wide$`2017`,
                         "2018_H" = total.q97.5.wide$`2017`,
                         "2019" = total.median.wide$`2019`,
                         "2019_L" = total.q2.5.wide$`2019`,
                         "2019_H" = total.q97.5.wide$`2019`,
                         "2020" = total.median.wide$`2020`,
                         "2020_L" = total.q2.5.wide$`2020`,
                         "2020_H" = total.q97.5.wide$`2020`)

```

Assuming that observed counts per 100 m represent the entire sectors, we extrapolated the estimated numbers to the entire sectors (Figure 2).

#### 2014
 The total number of hatchlings produced in 2014 ranged from ```r format(ceiling(min(total.median.wide[, "2014"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2014"] == min(total.median.wide[, "2014"], na.rm = T), "2014"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2014"] == min(total.median.wide[, "2014"], na.rm = T), "2014"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2014"] == min(total.median.wide[, "2014"], na.rm = T)])``` sector to ```r format(ceiling(max(total.median.wide[, "2014"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2014"] == max(total.median.wide[, "2014"], na.rm = T), "2014"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2014"] == max(total.median.wide[, "2014"], na.rm = T), "2014"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2014"] == max(total.median.wide[, "2014"], na.rm = T)])``` sector (Tables 1, 2, 3).  

#### 2015
The total number of hatchlings produced in 2015 ranged from ```r format(ceiling(min(total.median.wide[, "2015"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2015"] == min(total.median.wide[, "2015"], na.rm = T), "2015"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2015"] == min(total.median.wide[, "2015"], na.rm = T), "2015"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2015"] == min(total.median.wide[, "2015"], na.rm = T)])``` sector to ```r format(ceiling(max(total.median.wide[, "2015"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2015"] == max(total.median.wide[, "2015"], na.rm = T), "2015"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2015"] == max(total.median.wide[, "2015"], na.rm = T), "2015"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2015"] == max(total.median.wide[, "2015"], na.rm = T)])``` sector (Tables 1, 2, 3).  

#### 2016
The total number of hatchlings produced in 2016 ranged from ```r format(ceiling(min(total.median.wide[, "2016"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2016"] == min(total.median.wide[, "2016"], na.rm = T), "2016"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2016"] == min(total.median.wide[, "2016"], na.rm = T), "2016"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2016"] == min(total.median.wide[, "2016"], na.rm = T)])``` sector to ```r format(ceiling(max(total.median.wide[, "2016"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2016"] == max(total.median.wide[, "2016"], na.rm = T), "2016"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2016"] == max(total.median.wide[, "2016"], na.rm = T), "2016"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2016"] == max(total.median.wide[, "2016"], na.rm = T)])``` sector (Tables 1, 2, 3).  

#### 2017
In 2017, they ranged from ```r format(ceiling(min(total.median.wide[, "2017"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2017"] == min(total.median.wide[, "2017"], na.rm = T), "2017"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2017"] == min(total.median.wide[, "2017"], na.rm = T), "2017"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2017"] == min(total.median.wide[, "2017"], na.rm = T)])``` sector to ```r format(ceiling(max(total.median.wide[, "2017"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2017"] == max(total.median.wide[, "2017"], na.rm = T), "2017"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2017"] == max(total.median.wide[, "2017"], na.rm = T), "2017"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2017"] == max(total.median.wide[, "2017"], na.rm = T)])``` sector (Tables 1, 2, 3). 

#### 2018
In 2018, they ranged from ```r format(ceiling(min(total.median.wide[, "2018"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2018"] == min(total.median.wide[, "2018"], na.rm = T), "2018"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2018"] == min(total.median.wide[, "2018"], na.rm = T), "2018"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2018"] == min(total.median.wide[, "2018"], na.rm = T)])``` sector to ```r format(ceiling(max(total.median.wide[, "2018"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2018"] == max(total.median.wide[, "2018"], na.rm = T), "2018"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2018"] == max(total.median.wide[, "2018"], na.rm = T), "2018"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2018"] == max(total.median.wide[, "2018"], na.rm = T)])``` sector (Tables 1, 2, 3). 

#### 2019
In 2019, they ranged from ```r format(ceiling(min(total.median.wide[, "2019"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2019"] == min(total.median.wide[, "2019"], na.rm = T), "2019"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2019"] == min(total.median.wide[, "2019"], na.rm = T), "2019"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2019"] == min(total.median.wide[, "2019"], na.rm = T)])``` sector to ```r format(ceiling(max(total.median.wide[, "2019"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2019"] == max(total.median.wide[, "2019"], na.rm = T), "2019"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2019"] == max(total.median.wide[, "2019"], na.rm = T), "2019"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2019"] == max(total.median.wide[, "2019"], na.rm = T)])``` sector (Tables 1, 2, 3).


#### 2020
In 2020, they ranged from ```r format(ceiling(min(total.median.wide[, "2020"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2020"] == min(total.median.wide[, "2020"], na.rm = T), "2020"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2020"] == min(total.median.wide[, "2020"], na.rm = T), "2020"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2020"] == min(total.median.wide[, "2020"], na.rm = T)])``` sector to ```r format(ceiling(max(total.median.wide[, "2020"], na.rm = T)), big.mark = ",", trim = TRUE, scientific = FALSE)``` (95% CI = [```r format(ceiling(na.omit(total.q2.5.wide[total.median.wide[, "2020"] == max(total.median.wide[, "2020"], na.rm = T), "2020"])), big.mark = ",", trim = TRUE, scientific = FALSE)``` - ```r format(ceiling(na.omit(total.q97.5.wide[total.median.wide[, "2020"] == max(total.median.wide[, "2020"], na.rm = T), "2020"])), big.mark = ",", trim = TRUE, scientific = FALSE)```]) in the ```r na.omit(row.names(total.median.wide)[total.median.wide[, "2020"] == max(total.median.wide[, "2020"], na.rm = T)])``` sector (Tables 1, 2, 3).


```{r Table_total_median, echo=FALSE, warning=FALSE}
knitr::kable(total.median.wide, 
             digits = 0,
             format.args = list(big.mark = ",", scientific = FALSE),
             caption = "Median estimated total hatchling production per sector based on modified Richards' equations. ")
```


```{r Table_total_q2.5, echo=FALSE, warning=FALSE}
knitr::kable(total.q2.5.wide, 
             digits = 0,
             format.args = list(big.mark = ",", scientific = FALSE),
             caption = "Lower credibility limits of estimated total hatchling production per sector based on modified Richards' equations. ")
```


```{r Table_total_q97.5, echo=FALSE, warning=FALSE}
knitr::kable(total.q97.5.wide, 
             digits = 0,
             format.args = list(big.mark = ",", scientific = FALSE),
             caption = "Upper credibility limits of estimated total hatchling production per sector based on modified Richards' equations. ")
```

## Effects of reprofiling
To determine the effects of re-profiling the beach, the number of estimated hatchlings per 100 m was compared between 2014R and the South sector and between 2017R and the South sector.  The re-profiled areas (2014 and 2017) experience the same environmental effects and nesting activities as the South sector.  

```{r effects_reprofiling, echo=FALSE, include=FALSE, warning=FALSE}
Girondot.100m.summary <- Girondot_summary %>% 
  select(Season, q2.5, q50, q97.5, Sector) %>%
  mutate(SeasonNum = as.numeric(Season) + 2013)

Girondot.100m.summary[((Girondot.100m.summary$SeasonNum < 2017 |
                          Girondot.100m.summary$SeasonNum > 2018) & Girondot.100m.summary$Sector == "2017R"),
                   c("q2.5", "q50", "q97.5")] <- NA

Girondot.100m.summary[(Girondot.100m.summary$Sector == "2019R" & 
                          Girondot.100m.summary$SeasonNum < 2019), 
                       c("q2.5", "q50", "q97.5")] <- NA

Girondot.100m.summary[(Girondot.100m.summary$Sector == "West" & 
                          (Girondot.100m.summary$SeasonNum < 2017 |
                             Girondot.100m.summary$SeasonNum > 2018)), 
                       c("q2.5", "q50", "q97.5")] <- NA

Girondot.100m.summary %>% select(Season, q50, Sector) -> median_100m
Girondot.100m.summary %>% select(Season, q2.5, Sector) -> q2.5_100m
Girondot.100m.summary %>% select(Season, q97.5, Sector) -> q97.5_100m

median.100m.wide <- as.data.frame(reshape2::acast(median_100m, 
                                                   Sector ~ Season, 
                                                   value.var = "q50"))

q2.5.100m.wide <- as.data.frame(reshape2::acast(q2.5_100m, 
                                                 Sector ~ Season, 
                                                 value.var = "q2.5"))

q97.5.100m.wide <- as.data.frame(reshape2::acast(q97.5_100m, 
                                                  Sector ~ Season, 
                                                  value.var = "q97.5"))

#increase.2014R <- median.100m.wide["2014R",]/median.100m.wide["South",]

```



```{r Table_100m_median, echo=FALSE, warning=FALSE}
knitr::kable(median.100m.wide, 
             digits = 0,
             format.args = list(big.mark = ",", scientific = FALSE),
             caption = "Median estimated total hatchling production per 100 m based on modified Richards' equations. ")
```


```{r Table_100m_q2.5, echo=FALSE, warning=FALSE}
knitr::kable(q2.5.100m.wide, 
             digits = 0,
             format.args = list(big.mark = ",", scientific = FALSE),
             caption = "Lower credibility limits of estimated hatchling production per 100 m based on modified Richards' equations. ")
```


```{r Table_100m_q97.5, echo=FALSE, warning=FALSE}
knitr::kable(q97.5.100m.wide, 
             digits = 0,
             format.args = list(big.mark = ",", scientific = FALSE),
             caption = "Upper credibility limits of estimated hatchling production per 100 m based on modified Richards' equations. ")
```


```{r compute_increase, echo=FALSE, include=FALSE}
# To compute the uncertainty in the amount of increase in hatchling production, I need to find the number of
# hatchlings per season for 2014R, 2017R, and South sectors using all MCMC samples.
#Seasons_stats <- list(length = length(seasons))
i <- j <- k <- 1
#k <- 50
tmp.ratios.2014R <- tmp.ratios.2017R <- tmp.ratios.2019R <- matrix(data = NA, 
                                                                   ncol = length(seasons), 
                                                                   nrow = jm$mcmc.info$n.samples)

# obs.y = season x sectors x #days
# sectors = 2014R, 2017R, 2019R, North, South, West  

for (i in 1:length(seasons)){
  tmp.sectors <- matrix(data = NA, ncol = length(Sectors), nrow = jm$mcmc.info$n.samples)
  for (j in 1:length(Sectors)){
    tmp <- matrix(data = NA, ncol = n.days, nrow = jm$mcmc.info$n.samples)
    
    # For each day, estimated abundance is computed
    for (k in 1:n.days){
      tmp[,k] <- Girondot_fcn(d = k, 
                              S = extract.samples("S", jm$samples), 
                              K = extract.samples("K", jm$samples), 
                              P = extract.samples(paste0("P[", i, "]"), jm$samples), 
                              min = 1, 
                              max = extract.samples(paste0("max[", i, ",", j, "]"), jm$samples)) 
      
    
    }
    
    tmp.sectors[, j] <- rowSums(tmp)
  }
  
  # the order of these need to be confirmed... 
  tmp.ratios.2014R[, i] <- tmp.sectors[, 1]/tmp.sectors[, 5]
  tmp.ratios.2017R[, i] <- tmp.sectors[, 2]/tmp.sectors[, 5]
  tmp.ratios.2019R[, i] <- tmp.sectors[, 3]/tmp.sectors[, 5]
  
}

# Compute the quantiles of increase for each year 
stats.ratios.2014R <- data.frame(apply(tmp.ratios.2014R, 
                                       MARGIN = 2, 
                                       FUN = quantile, 
                                       c(0.025, 0.5, 0.975)))
colnames(stats.ratios.2014R) <- c("2014", "2015", "2016", "2017", "2018", "2019", "2020")

# Although I compute stats for all years, only 2017 matters for the 2017R sector
stats.ratios.2017R <- data.frame(apply(tmp.ratios.2017R, MARGIN = 2, FUN = quantile, c(0.025, 0.5, 0.975)))
colnames(stats.ratios.2017R) <- c("2014", "2015", "2016", "2017", "2018", "2019", "2020")

stats.ratios.2017R %>% select(c("2017", "2018", "2019", "2020")) -> stats.ratios.2017R

# Although I compute stats for all years, only 2019 matters for the 2019R sector
stats.ratios.2019R <- data.frame(apply(tmp.ratios.2019R, MARGIN = 2, FUN = quantile, c(0.025, 0.5, 0.975)))
colnames(stats.ratios.2019R) <- c("2014", "2015", "2016", "2017", "2018", "2019", "2020")

```

The reprofiled sectors consistently produced more hatchlings than the unmodified South sector over the four year period (Tables 4, 5, 6). The increase in hatchling productions in the 2014R sector ranged from ```r format(signif(min(stats.ratios.2014R["50%",]), digits = 3), nsmall = 2)``` (95% CI = [```r format(signif(stats.ratios.2014R["2.5%", stats.ratios.2014R["50%", ] == min(stats.ratios.2014R["50%",])], digits = 3), nsmall = 2)``` - ```r format(signif(stats.ratios.2014R["97.5%", stats.ratios.2014R["50%", ] == min(stats.ratios.2014R["50%",])], digits = 3), nsmall = 2)```]) in ```r colnames(stats.ratios.2014R)[stats.ratios.2014R["50%", ] == min(stats.ratios.2014R["50%",])]``` to ```r format(signif(max(stats.ratios.2014R["50%",]), digits = 3), nsmall = 2)``` (95% CI = [```r format(signif(stats.ratios.2014R["2.5%", stats.ratios.2014R["50%", ] == max(stats.ratios.2014R["50%",])], digits = 3), nsmall = 2)``` - ```r format(signif(stats.ratios.2014R["97.5%", stats.ratios.2014R["50%", ] == max(stats.ratios.2014R["50%",])], digits = 3), nsmall =2 )```]) in ```r colnames(stats.ratios.2014R)[stats.ratios.2014R["50%", ] == max(stats.ratios.2014R["50%",])]``` (Table 7).  

```{r Table_increase_2014R, echo=FALSE, warning=FALSE}
knitr::kable(stats.ratios.2014R, 
             digits = 2,
             format.args = list(big.mark = ",", scientific = FALSE),
             caption = "Amount of increase in hatchling productions at the 2014R sector compared with the South sector.")
```

The increase in hatchling productions in the 2017R sector ranged from ```r format(signif(min(stats.ratios.2017R["50%",]), digits = 3), nsmall = 2)``` (95% CI = [```r format(signif(stats.ratios.2017R["2.5%", stats.ratios.2017R["50%", ] == min(stats.ratios.2017R["50%",])], digits = 3), nsmall = 2)``` - ```r format(signif(stats.ratios.2017R["97.5%", stats.ratios.2017R["50%", ] == min(stats.ratios.2017R["50%",])], digits = 3), nsmall = 2)```]) in ```r colnames(stats.ratios.2017R)[stats.ratios.2017R["50%", ] == min(stats.ratios.2017R["50%",])]``` to ```r format(signif(max(stats.ratios.2017R["50%",]), digits = 3), nsmall = 2)``` (95% CI = [```r format(signif(stats.ratios.2017R["2.5%", stats.ratios.2017R["50%", ] == max(stats.ratios.2017R["50%",])], digits = 3), nsmall = 2)``` - ```r format(signif(stats.ratios.2017R["97.5%", stats.ratios.2017R["50%", ] == max(stats.ratios.2017R["50%",])], digits = 3), nsmall =2 )```]) in ```r colnames(stats.ratios.2017R)[stats.ratios.2017R["50%", ] == max(stats.ratios.2017R["50%",])]``` (Table 8).   

```{r Table_increase_2017R, echo=FALSE, warning=FALSE}
knitr::kable(stats.ratios.2017R, 
             digits = 2,
             format.args = list(big.mark = ",", scientific = FALSE),
             caption = "Amount of increase in hatchling productions at the 2017R sector compared with the South sector.")
```
